From Net-Zero to Net-Negative: Assessing \hydrogen{} and \carbon{} Network Strategies in Europe

### 2023-10-23 report/submissions/journal/paper/paper.tex
add more plots (diff, heatmap, capacity country)

\title{Designing a \carbon{} Network for a Net-Zero European Energy System}

@@

%
The PyPSA-Eur model integrates exogenous assumptions for energy demand on an hourly basis, the annual sums of which are shown in figure~\ref{fig:total-demand-bar}. Among those, the energy demand time-series for power, transport, heat, gas at rural, urban and industrial sites as well as for the agriculture sector are defined per region. Additionally, demands for kerosene for aviation, methanol for shipping as well of naphta for industry are aggregated and must be met by the sum of all regional supplies.
Taking non-abatable emissions from fossil-based industrial processes into account, the system emits of 152~Mt \carbon{} per year, which can optionally be captured through corresponding investments.

>>>>

\title{From Net-Zero to Net-Negative: Assessing \hydrogen{} and \carbon{} Network Strategies in Europe}

@@

%
The PyPSA-Eur model integrates exogenous assumptions for energy demand on an hourly basis, the annual sums of which are shown in figure~\ref{fig:total-demand-bar}. Among those, the energy demand time-series for power, transport, heat, gas at rural, urban and industrial sites as well as for the agriculture sector are defined per region. Additionally, demands for kerosene for aviation, methanol for shipping as well of naphta for industry are aggregated and must be met by the sum of all regional supplies.
Taking non-abatable emissions from fossil-based industrial processes, aviation, shipping and agriculture into account, the system emits of 633~Mt \carbon{} per year, 153~Mt of which are industrial emissions which can optionally be captured through corresponding investments.
